%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Sole Developer} % Affiliation/role
    {\href{https://github.com/alexispurslane/atomicdatabase}{Atomic Database}}
    {}
    {Apr. 1, 2019 - Jul. 22, 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Created a proof-of-concept database using a \textbf{lazy backtracking/logic programming query system with a natural language front-end} using Rust from scratch (v3.0) and Python generators (v2.0).}
      \end{cvitems}
    }

    \cventry
    {Sole Developer} % Affiliation/role
    {\href{https://github.com/alexispurslane/fides}{Fides: Distributed Trust Application}}
    {}
    {Feb. 15, 2020 - May 19, 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Created a \textbf{prototype social network designed to provide distributed reputation tracking through arbitrated and horizontal contracts}, using React.JS, Redux, and TypeScript.}
      \end{cvitems}
    }

    \cventry
    {Sole Developer} % Affiliation/role
    {\href{https://github.com/alexispurslane/bloc}{Bloc WIP}}
    {}
    {Aug. 26, 2023 - } % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Designing and programming a sleek native \textbf{alternative Android app for self-hosted or official instances of the OSS Discord clone Revolt} using Jetpack Compose, Kotlin, and official Google Developer best practices.}
      \end{cvitems}
    }

    \cventry
    {Sole Developer}
    {\href{https://github.com/alexispurslane/embryo-engine}{Embryo Engine WIP}}
    {}
    {Jan. 21, 2023 - }
    {
      \begin{cvitems}
        \item {Working on a data-oriented, scriptable entity-component-system-based game engine using Rust, raw OpenGL, and SDL2, focused on helping indie programmers build retro immersive sims and open world RPGs.}
      \end{cvitems}
    }

    \cventry
    {Sole DevOps Engineer}
    {Self-Hosted Services}
    {}
    {Jan. 01, 2023 - }
    {
      \begin{cvitems}
        \item {Creating and maintaining five secure self-hosted container services on a \textbf{Fedora CoreOS system using Podman, Podman-Compose, and Ignition, with SELinux enabled} for friends and family.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
